---
title: "SectionB"
author: "xiaoyi"
date: "16/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# SectionB
```{r}
library(tidyverse)
library(ggplot2)
```
## B.1
### (a)
```{r}
c_prob_person_given_alarm<-function(p0,p1,q){
  phi = p1*q/(p0*(1-q)+p1*q)
  return (phi)
}
```
### (b)
Let A denotes the event that the sensor makes a sound, let B denotes the event that no person present, let C denotes the event that at least one person present.
we can express the events in the question as below:
$P(A\mid B)=p_{0}$ ,$P(A\mid C)=p_{1}$,$P(C)=q$,$P(C\mid A)=\varPhi$
we know that Bayes theorem formula is $ \frac{P(A\mid B)=P(B\mid A)\cdotp(A)}{P(B)}$
so we have the following formulas based on the questions:
$P(A\mid C)=P(C\mid A)\cdot \frac{P(A)}{P(C)} \Rightarrow P(C\mid A)=\frac{p_{1}q}{P(A)}$
$P(B\mid A)=P(A\mid B)\cdot \frac{P(B)}{P(A)} \Rightarrow p_{0}\cdot \frac{1-q}{P(A)}$
because the complement of event 'no person' is the event  'at least one person', we get this formula
$P(B\mid C)=1-P(A\mid C)$
we can calculate $P(A)=p_{0}(1-q)+p_{1}q$
hence,
$\varPhi=P(C\mid A)=\frac{p_{1}q}{P(A)}=\frac{p_{1}q}{p_{0}(1-q)+p_{1}q}$

```{r}
p0<- 0.05
p1<- 0.95
q<- 0.1
c_prob_person_given_alarm(p0,p1,q)
```
### (c)
```{r}
p0<-0.05
p1<-0.95
q<- seq(0,1,0.001)
result = data.frame(phi = c_prob_person_given_alarm(p0,p1,q))
#result 
ggplot(data = result, aes(x = q, y = phi))+
  geom_line()+
  labs(y = expression(Phi))+
  theme_bw()
```

## B.2
### (a)
\[
\begin{equation}
  p_{X}(x) =
  \begin{cases}
    1-\alpha-\beta-\gamma &\text{if } x = 0 \\
    \alpha & \text{if }x = 1 \\
    \beta & \text{if }x = 2  \\
    \gamma & \text{if }x = 5 \\
    0  &\text{otherwise}
  \end{cases}
\end{equation}
\]

### (b)
\[
\mathbb{E}(X)= \sum_{x\in \mathbb{R}} x\cdot p_{X}(x) 
= 1\cdot \alpha+2\cdot \beta+5\cdot \gamma+0\cdot (1-\alpha-\beta-\gamma)+
\sum_{x\in \mathbb{R}\backslash\text{{0,1}}}x \cdot p_{X}(x)
=\alpha+2\beta+5\gamma
\]

### (c)
\[
Var(X)=\mathbb{E}[\{X-\mathbb{E}(X)\}^2]=
\sum_{x\in \mathbb{R}} p_{X}(x)\cdot (x-(\alpha +2\beta+ 5\gamma))^2
=\mathbb{E}[X^2]-\mathbb{E}[X]^2
=-\alpha^2-4\alpha\beta-10\alpha\gamma-4\beta^2-20\beta\gamma-25\gamma^2+\alpha+4\beta+25\gamma
\]


### (d)
\[
\mathbb{E}(\bar X)=\mathbb{E}(\frac{1}{n}\sum_{i=1}^{n}X_{i})=\frac{1}{n}\cdot \sum_{i=1}^{n}\mathbb{E}(X_{i})
=\frac{1}{n}\sum_{i=1}^{n}(\alpha+2\beta+5\gamma)=\alpha+2\beta+5\gamma
\]

### (e)
\[
Var(\bar X)=Var(\frac{1}{n}\sum_{i=1}^{n}X_{i})=(\frac{1}{n})^2\cdot \sum_{i=1}^{n}Var(X_{i})=\frac{-\alpha^2-4\alpha\beta-10\alpha\gamma-4\beta^2-20\beta\gamma-25\gamma^2+\alpha+4\beta+25\gamma}{n}
\]

### （d)

```{r}

var<-function(a,b,r)
  {
  c=(-a^2-4*a*b-10*a*r-4*b^2-20*b*r-25*r^2+a+4*b+25*r)
  return(c)
}

b=var(0.1,0.2,0.3)


```


```{r}
# Assignment5
# use the uniform distribution to simulate data from the discrete random variable

sample_X_0125<-function(n,alpha,beta,gamma){
  sample_X<-data.frame(U = runif(n))%>%
    mutate(X = case_when(
      (0 <= U)&(U < alpha)~1,
      (alpha <= U)&(U < alpha+beta)~2,
      (alpha+beta <= U)&(U < alpha+beta+gamma)~5,
      (alpha+beta+gamma <= U)&(U <= 1)~0))%>%
    pull(X)
  return (sample_X)
}
```
### (e)
```{r}
set.seed(1006)
n<-100000
alpha<-0.1
beta<-0.2
gamma<-0.3
sample_X<-sample_X_0125(n,alpha,beta,gamma)
#sample_X
mean(sample_X)
var(sample_X)
```
I observe the value for $\bar X$is 1.99478, the value for sample variance is 4.391097, this is not exactly the same as expected in question(b)and(c).
Here are the reasons:
Based on my answer to question(b), we have $\mathbb{E}(X)=\alpha+2\beta+5\gamma=2$, Moreover, in light of the law of large numbers of n, we expect the sample average to be close to the expectation for large samples of independent and identically
distributed random variables.

By question (c) we have Var(X) = $=-\alpha^2-4\alpha\beta-10\alpha\gamma-4\beta^2-20\beta\gamma-25\gamma^2+\alpha+4\beta+25\gamma=4.4$. Hence, the
sample variance is close to the population variance.

### (h)
```{r}
set.seed(1006)
trial<-seq(10000)
n<-100

alpha<-0.1
beta<-0.2
gamma<-0.3
simulation_df<-data.frame(trail)%>%
  mutate(sample = map(.x=trial, .f = ~sample_X_0125(n,alpha,beta,gamma)))%>%
  mutate(sample_mean = map_dbl(.x=sample, .f = mean))


```
```{r}
simulation_df%>%head(5)
```


### (i)
```{r}
simulation_df%>%
  

ggplot()+
  ggtitle("The histogram of sample mean") +
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram(aes(x=sample_mean),binwidth = 0.02)
```
### (j)
```{r}
sample_mean_expectation<-round(mean(simulation_df$sample_mean),digits = 4)
sample_mean_variance<-round(var(simulation_df$sample_mean),digits = 4)
sample_mean_expectation
sample_mean_variance
```
The numerical value of the expectation $\mathbb{E}(\bar X)$ is 1.9988, the numerical value of the variance $Var(\bar X)$ is 0.0444.

### (k)
```{r}
mu<-sample_mean_expectation
sigma<-sqrt(sample_mean_variance)
x_min<-mu-4*sigma
x_max<-mu+4*sigma
inc<-0.0001
rescaled_gaussian_df<-data.frame(x=seq(x_min,x_max,inc))%>%
  mutate(pdf=200*map_dbl(.x=x,.f=~dnorm(x=.x,mean=mu,sd=sigma)))
# 200 or 10000?

colors<-c("Gaussian pdf"="red","sample_mean_histogram"="blue")
fill<-c("Gaussian pdf"="white","sample_mean_histogram"="white")


ggplot()+
  geom_histogram(data=simulation_df,
                 aes(x=sample_mean,colour = "sample_mean_histogram",fill = "sample_mean_histogram"),
                 binwidth = 0.02,size = 0.3)+
  geom_line(data=rescaled_gaussian_df,
            aes(x,y=pdf,color="Gaussian pdf"),size=1)+
  scale_color_manual(name = "", values=colors)+
  scale_fill_manual(name = "", values=fill)+
  theme_bw()
```

### (l)
the shape of this histogram essentially  matches the rescaled version of the probability density function of a Gaussian random(when scale factor is 200)

The central limit theorem (CLT) states that the distribution of sample means approximates a gaussian distribution as the sample size gets larger, regardless of the population's distribution.